Import and Tidy ADFG Supplied Location and Haul-out Data

### 2021-06-29 analysis/paper/paper.Rmd
UPDATED DATA AND RE-RUN MODELS
at this point the ADFG and NSB collaborative data have been incorporated and models re-run.

dat.sf <- sf::st_read(con,query = qry) %>% 
  filter(lubridate::yday(haulout_dt) < 197 ) %>% 
  mutate(age = case_when(
    age == "PUP" ~ "YOUNG OF YEAR",
    age == "YEARLING" ~ "SUBADULT",
    TRUE ~ age
  ))

deploy_meta <- tbl(con, in_schema("telem", "tbl_tag_deployments")) %>% 
  filter(speno %in% !!unique(dat.sf$speno)) %>% 
  group_by(speno) %>% 
  summarise(deploy_dt = min(deploy_dt, na.rm = TRUE)) %>% 
  collect()

>>>>

dat.sf <- sf::st_read(con,query = qry) %>% 
  filter(lubridate::yday(haulout_dt) < 197 ) %>% 
  mutate(age = case_when(
    age %in% c("pup", "PUP") ~ "YOUNG OF YEAR",
    age %in% c("yearling","YEARLING","subadult","Subadult") ~ "SUBADULT",
    age %in% c("adult","ADULT","Adult") ~ "ADULT",
    TRUE ~ age),
    species = case_when(
    species == "bearded" ~ "Bearded seal",
    species == "spotted" ~ "Spotted seal",
    TRUE ~ species),
    sex = case_when(
    sex %in% c("Female","female") ~ "F",
    sex %in% c("Male","male") ~ "M",
    TRUE ~ sex)
    ) %>% 
  filter(!is.na(age))

load(here::here('data/locs_sf.Rdata'))

deploy_meta <- locs_sf %>% 
  as_data_frame() %>% 
  select(speno, deploy_dt) %>% 
  filter(speno %in% !!unique(dat.sf$speno)) %>% 
  group_by(speno) %>% 
  summarise(deploy_dt = min(deploy_dt, na.rm = TRUE))

### 2021-06-29 data_raw/adfg/adfg_tidydata.Rmd
UPDATED DATA AND RE-RUN MODELS
at this point the ADFG and NSB collaborative data have been incorporated and models re-run.

adfg_deployments <- readr::read_csv('ADFG_SealDeploymentTable3.csv',
                                    col_types = adfg_deploy_cols) %>% 
  dplyr::mutate(DateTagged = lubridate::force_tz(DateTagged, 
                                                 'America/Anchorage')) %>% 
  dplyr::mutate(DateTagged = lubridate::as_date(DateTagged, 
                                                tz = 'America/Anchorage'))

>>>>

adfg_deployments <- readr::read_csv('ADFG_SealDeploymentTable3.csv',
                                    col_types = adfg_deploy_cols) %>% 
  dplyr::mutate(DateTagged = lubridate::force_tz(DateTagged, 
                                                 'America/Anchorage')) %>% 
  dplyr::mutate(DateTagged = lubridate::as_datetime(DateTagged, 
                                                tz = 'America/Anchorage'))
